Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}

### 2017-11-06 paper/supplemental/leftcylinder.tex
Latest updates including supplemental for submission and the arXiv versions.
Update supplemental material.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/datasets.pdf}
\caption{The five different datasets we use for evaluation. The top row shows the first slice of the AC4 and L.~Cylinder mouse brain datasets as reported in the paper. The bottom row shows the first slice of the CREMI A/B/C fruit fly datasets which we used for additional experiments.}
\label{fig:datasets}
\end{figure}

@@

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/datasets.png}
\caption{The five different datasets we use for evaluation. The top row shows the first slice of the AC4 and L.~Cylinder mouse brain datasets as reported in the paper. The bottom row shows the first slice of the CREMI A/B/C fruit fly datasets which we used for additional experiments.}
\label{fig:datasets}
\end{figure}

@@

\section{Confirmatory Data Analysis}

\CHANGED{In the paper, we use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}

\CHANGED{\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome. Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$]. This means that novices using GP perform significantly better than using FP and Dojo.
A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]). For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]). The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$]. However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}

\CHANGED{\paragraph{L. Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]). The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}
